% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zhuo Ying Jiang Li}

\basicInfo{
  % (+44) 07740271205 $\bullet$
  % \href{mailto:zyj20@cam.ac.uk}{zyj20@cam.ac.uk}
  zyj20 [at] cl.cam.ac.uk
  \href{https://github.com/RoundofThree}{GitHub ID: RoundofThree}
%  \href{https://www.linkedin.com/in/zhuo-ying-jiang-li-56957418a/}{Linkedin}
}

\section{Education}
\datedsubsection{\textbf{\href{https://www.cam.ac.uk/}{University of Cambridge}}, Cambridge, UK}{10/2023 -- 06/2026 (expected)}
PhD in Computer Science, focusing on vulnerability research and adversarial analysis in CHERI software. \\
Thesis proposal: \textit{The Art of Exploitation in CHERI-Enabled Systems and Applications}

\datedsubsection{\textbf{\href{https://www.cam.ac.uk/}{University of Cambridge}}, Cambridge, UK}{10/2022 -- 06/2023}
MPhil in Advanced Computer Science. % \textit{Advanced Topics in Computer Architecture, Advanced Operating Systems, Computer Security: Principles and Foundations, Principles of Machine Learning Systems, Mobile Health} \\
Graduated with First Class (Distinction).
\datedsubsection{\textbf{\href{https://www.kcl.ac.uk/}{King's College London}}, London, UK}{09/2019 -- 06/2022}
BSc Computer Science. % \textit{Information Security, Cryptography, Operating Systems, Internet Systems, Compilers, Foundations of Computing (Maths),
% C++ for algorithms and data structures, Optimization Methods, Artificial Intelligence} \\
Graduated with First Degree with Honours.
% \datedsubsection{\textbf{IES Son Pacs}, Balearic Islands, Spain}{09/2017 -- 06/2019}
% International Baccalaureate. Grade: 45/45, Extended Essay (Maths): A

% -----------------------------------------------------------

\section{Selected Projects}

\datedsubsection{\textbf{Syzkaller: Kernel fuzzing for CheriBSD}}{07/2024 - 09/2024}
\begin{itemize}
  \item Ported syzkaller to fuzz CheriBSD pure-capability kernel in Arm Morello. Arm Morello is a prototype System-on-Chip (SoC) with a CHERI-extended ARMv8-A processor.
  \item Added support to syzkaller for fuzzing bluetooth, netlink and netgraph kernel subsystems.
  \item Found several security bugs applicable to FreeBSD, conducted an analysis of them, and wrote proof-of-concept triggers. One bug is pending a security advisory.
  \item Worked in a dynamic two-person team, contributing ideas and fostering a collaborative environment.
\end{itemize}

\datedsubsection{\textbf{AFL++ for CheriABI}}{11/2024 - Ongoing}
\begin{itemize}
  \item Ported AFL++ to CheriABI. Specifically, LLVM PCGUARD instrumentation.
  \item Set up fuzzing harnesses for userspace programs in CheriABI. Work in progress.
\end{itemize}

\datedsubsection{\textbf{CHERI+ASan: AddressSanitizer for CheriABI}}{09/2024 - 12/2024}
\begin{itemize}
  \item Ported LLVM AddressSanitizer (ASan) runtime to CheriABI in CheriBSD Arm Morello. The goal is to enhance sanitization performance and effectiveness by combining deterministic spatial safety detection of CHERI and redzone-based temporal safety detection of ASan.
  \item Ported Kernel AddressSanitizer (KASAN) to CheriBSD pure-capability kernel in Arm Morello. 
  \item Improved KASAN memory corruption detection in CheriBSD by implementing kernel allocation quarantining and redzone padding. Also applicable to FreeBSD.
\end{itemize}

% \datedsubsection{\textbf{Proofs-of-concept of Past Vulnerabilities in the CheriBSD Kernel}}{02/2024 - Ongoing}
% \begin{itemize}
%   \item Maintaining a framework of exploit primitives and their preconditions given CHERI-based security mitigations.
%   \item Maintaining a vulnerable fork of the CheriBSD kernel with backpatched real-world vulnerabilities.
%   \item Developed individual \textit{proofs-of-concept} programs to prove the feasibility of exploitation techniques against the CheriBSD kernel given constraints.
% \end{itemize}

\datedsubsection{\textbf{Damn Vulnerable Kernel Module for CheriBSD}}{04/2024 - Ongoing}
\begin{itemize}
  \item Developed a tool that provides a flexible way to inject exploitation primitives in a controlled adversarial experiment, which serves as a swiss army knife for demonstrating and evaluating exploitation techniques with controlled attacker capabilities.
\end{itemize}

\datedsubsection{\textbf{Open-source Binary Analysis Tools for the Morello Architecture}}{11/2023 - Ongoing}
\begin{itemize}
  \item Developed Ghidra Software Reverse Engineering suite Arm Morello architecture extension.
  \item Developed GEF (GDB Enhanced Features) with Morello support: GDB plugins with visualisation commands of the heap state and program states.
  \item Developed Unicorn Engine with Morello support: scriptable CPU emulation library based on QEMU and with Python bindings.
\end{itemize}

% Compiler optimizations security CHERI
\datedsubsection{\textbf{Validation of CHERI IR Security Properties in LLVM Optimization Passes}}{11/2022 - 06/2023}
\begin{itemize}
  \item Proposed the CHERI Alive2 IR semantics model, modified from the Alive2 IR semantics model to conform to the CHERI C memory model assuming a purecap CheriABI runtime. The CHERI Alive2 IR semantics model has modified semantics for capability operations and memory accesses through capabilities as well as new undefined behaviour cases related to CHERI exceptions.
  % \item Proposed the concept of \textit{security refinements} and showed its relevance in validating the preservation of security semantics. 
  \item Implemented the CHERI Alive2 fork of Alive2 that adds support for CHERI intrinsics and attributes emitted by the Morello LLVM compiler, replaces the pointer type to the capability type in the underlying SMT encoding and models the proposed CHERI LLVM IR semantics and refinement checks. 
  \item Modified two compiler fuzzers to generate less conservative random programs in C and LLVM IR that cover pointer operations, pointer escaping, memory operations and CHERI-specific intrinsics and builtins.
  % \item Propose and test new optimization passes and/or modify existing optimization passes which exploit CHERI invariants to improve performance. 
  % \item Evaluate performance and code size of each optimization pass and evaluate on real-world applications (Nginx, maybe OpenSSL) under different optimization levels. 
\end{itemize}

% TASO with Apache TVM integration
\datedsubsection{\textbf{TASO-TVM: A Multi-Platform Tensor Algebra SuperOptimizer for Deep Learning}}{11/2022 - 1/2023}
\begin{itemize}
  \item Designed a architecture that integrates the TVM backend to the TASO superoptimizer. 
  \item Implemented the kernels and their cost model using AutoScheduler. 
  \item Evaluated the runtime performance of deep learning networks (BERT, NasRNN) using the autoscheduled kernels on different architectures (Metal, CUDA and CPU). 
\end{itemize}

% Adversarial poisoning
% \datedsubsection{\textbf{Targeted and targeted backdoor poisoning attacks against Drebin under
% problem-space derived constraints}}{11/2021 - 04/2022}
% \begin{itemize}
%   \item Presented and implemented a custom gradient-based attack algorithm in Python to perform targeted attacks under previously identified feature-space constraints for Drebin.
%   \item Adapted the \textit{watermarking} targeted backdoor attack method, proposed in a paper about image classification backdoor attacks, to Drebin. Implemented the backdoor attack using the genetic algorithm with greedy heuristics.
%   \item Evaluated and compared the different poisoning attack approaches, both targeted and targeted backdoor attacks, using the presented algorithms, to attack Drebin.
% \end{itemize}

% Regex matching engine: Brozowski algorithm based on derivatives
% \datedsubsection{\textbf{Regular expression matcher, lexer, parser and LLVM compiler front-end}}{09/2021}
% \begin{itemize}
%   \item Derived and proved the correctness of the Brzozowski derivatives for extended regular expression operations.
%   \item Implemented the Brzozowski algorithm in a functional language (Scala).
%   \item Implemented the Sulzmann \& Lu algorithm as an extension for regular expression lexing (Scala).
%   \item Implemented a parser and a compiler front-end that emits code in SSA form (LLVM IR). 
% \end{itemize}

% -----------------------------------------------------------

\section{Experience}

\datedsubsection{\textbf{CTF competitions}}{}
\begin{itemize}
  \item I mostly solve binary exploitation and reverse engineering challenges with the \textit{cheriPI} team at Cambridge. Some of the CTFs I have attended are PwnEd Qualifiers and Finals CTF, LakeCTF Qualifiers and Finals, CSAW, HackTheBox University CTF, Country2Country.
\end{itemize}

\datedsubsection{\textbf{Cambridge Cyber Security Society committee member}}{}
\begin{itemize}
  \item Organised socials to engage with other university members who are also into systems and security.
  \item Proposed ideas and organised academic workshops to foster interest into practical adversarial exploration and CHERI.
\end{itemize}

% \datedsubsection{\textbf{\href{https://www.sans.org/}{GIAC Hacker tools, techniques, exploits and incident handling training}}, SANS Institute}{Remote}
% \begin{itemize}
%   \item Studied in detail defensive and offensive operations in internal networks.
% \end{itemize}

% \datedsubsection{\textbf{Student Representative}}{King's College London}
% \begin{itemize}
%   \item Co-chaired the Student Staff Liaison Committee (SSLC).
%   \item Collected student feedback and discussed solutions with university staff.
%   \item Proposed ideas and organised events to improve the learning environment of the student community.
% \end{itemize}

% \datedsubsection{\textbf{SnapSense}}{Remote}
% \datedsubsection{Software Developer}{03/2021}
% \begin{itemize}
%   \item Implemented a diabetes ulcer monitoring system using Ruby on Rails
%   \item Deployed resources and backend server to AWS using S3, RDS and EB cloud services
% \end{itemize}

% \datedsubsection{\textbf{\href{https://www.kclcssa.com/}{King's College London Chinese Students and Scholars Association}}}{Remote}
% \datedsubsection{Software Developer}{09/2020}
% \begin{itemize}
%     \item Built a WeChat miniprogram for news, weather, restaurant listing, second hand exchange, events and more
%     \item Added support for one-click event booking
% \end{itemize}

% -----------------------------------------------------------

% \section{Selected Awards}
% \begin{itemize}
%     \item Alan Fairbourn Memorial Prize (most meritorious Final Year Project in the
%     Department of Informatics)\hfill 2022
%     \item Undergraduate Informatics BSc Finalist Prize (best performance during the final year of the BSc Computer Science programmes)\hfill 2022
%     \item Undergraduate Informatics Top-Performing Graduate (best overall performance over the duration of study in the
%     Department of Informatics for an undergraduate finalist)\hfill 2022
%     \item GIAC Advisory Board member (top performance)\hfill 2020
%     \item Undergraduate Informatics Year 1 or Year 2 Prize (best performance)\hfill 2020
%     \item Silver Prize, Iberoamerican Olympiad in Chemistry\hfill 2019
%     \item Silver Prize, National Olympiad in Chemistry\hfill 2019
%     \item Silver Prize, National Olympiad in Physics\hfill 2019
% \end{itemize}

% -----------------------------------------------------------

% \section{Publications and Articles}
% \begin{itemize}
%     % \item Shihong Song*, \textbf{Jiayi Weng}*, Hang Su, Dong Yan, Haosheng Zou, and Jun Zhu, ``Playing FPS Game with Environment-aware Hierarchical Reinforcement Learning,'' in \textbf{IJCAI'19 (oral)}, \href{https://trinkle23897.github.io/cv/viz2018.html}{[Page]} \href{https://www.ijcai.org/proceedings/2019/0482.pdf}{[PDF]}
%     % \item \textbf{Jiayi Weng}, Tsung-Yi Ho, Weiqing Ji, Peng Liu, Mengdi Bao, and Hailong Yao,  ``URBER: Ultrafast Rule-Based Escape Routing Method for Large-Scale Sample Delivery Biochips,'' in \textbf{TCAD'18}, \href{https://trinkle23897.github.io/cv/urber.html}{[Page]} \href{https://ieeexplore.ieee.org/document/8552446}{[PDF]}
% \end{itemize}

% -----------------------------------------------------------

\section{Skills}
\textbf{Programming Languages:} \small C/C++, Python.

\textbf{Others:} \small LLVM compiler hacking, UNIX kernel development, vulnerability research, reverse engineering, gdb.

\end{document}
